 

### 2021-03-12 doc/manuscript/tables_figures/tables.Rmd
improve hypothesis table

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypotheses <- read.csv("hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
hypotheses_table <- subset(hypotheses, select = -c(category, percent.sites, percent.species.site.combinations) ) #drop MAT column, plus columns with sd
kable(hypotheses_table, format = "latex", booktabs = TRUE,  escape = F)%>%

@@

  pack_rows("Annual growth is jointly influenced by water, temperature, DBH, and time. ", 1, 2, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Drought limits tree growth, but the response to water is nonlinear.", 3, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Temperature has predominantly negative, nonlinear effects on growth.", 6, 9, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("DBH", 10, 13, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%

  kable_styling(latex_options = c( "hold_position", "repeat header"), protect_latex = T, font_size = 7)

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypotheses <- read.csv("hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
hypotheses_table <- subset(hypotheses, table_row > 0, select=c(hypothesis, supported)) # subset to include only records flagged with include ==1, keeping columns to plot
rownames(hypotheses_table) <- c() # removes row names (original row numbers) on hypothesis table
colnames(hypotheses_table) = c("hypotheses and specific predictions","frequency observed")

kable(hypotheses_table, format = "latex", booktabs = TRUE,  escape = F)%>%

@@

  #pack_rows("Annual growth is simultaneously influenced by water, temperature, DBH, and time. ", 1, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("How does climate shape tree growth? ", 1,12, latex_gap_space = "1em", italic= TRUE)%>%
  row_spec(c(1,5,10), bold = T) %>%
  add_indent(c(2:4, 6:9,11:12)) %>%
  pack_rows("How does growth rate vary as trees grow?", 13,17,italic= TRUE, latex_gap_space = "1em", hline_before = FALSE)%>%
  row_spec(c(13), bold = T) %>%
  add_indent(c(14:17)) %>%
  pack_rows("How have growth rates changed through time?", 18,21,italic= TRUE, latex_gap_space = "1em", hline_before = FALSE)%>%
  row_spec(c(18), bold = T) %>%
  add_indent(c(19:21)) %>%

  kable_styling(latex_options = c( "hold_position"), protect_latex = T, font_size = 7)
